# Tournament selection

Results for the tournament selection parameter sweep on the diagnostics with no valleys.

## Data setup

```{r tor-data-setup, message=FALSE}
over_time_df <- read.csv(paste(DATA_DIR,'OVER-TIME/tor.csv', sep = "", collapse = NULL), header = TRUE, stringsAsFactors = FALSE)
over_time_df$T <- factor(over_time_df$T, levels = TS_LIST)

best_df <- read.csv(paste(DATA_DIR,'BEST/tor.csv', sep = "", collapse = NULL), header = TRUE, stringsAsFactors = FALSE)
best_df$T <- factor(best_df$T, levels = TS_LIST)

sati_df <- read.csv(paste(DATA_DIR,'SOL-FND/tor.csv', sep = "", collapse = NULL), header = TRUE, stringsAsFactors = FALSE)
sati_df$T <- factor(sati_df$T, levels = TS_LIST)
```

## Exploitation rate results

Here we present the results for **best performances** found by each selection scheme parameter on the exploitation rate diagnostic.
50 replicates are conducted for each scheme explored.

### Performance over time

Best performance in a population over time.
Data points on the graph is the average performance across 50 replicates every 2000 generations.
Shading comes from the best and worse performance across 50 replicates.

```{r tor-exp-per-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'exp') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

over_time_plot = ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )

over_time_plot
```

```{r tor-legend, echo=FALSE}
legend <- cowplot::get_legend(
  over_time_plot +
    guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
    )
)
```

### Generation satisfactory solution found

First generation a satisfactory solution is found throughout the 50,000 generations.

```{r tor-exp-ssf, warning=FALSE, out.width="100%"}
plot = filter(sati_df, acro == 'exp') %>%
  ggplot(., aes(x = T, y = gen , color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Generation",
    limits=c(2000, 12000),
    breaks=c(2000, 4000, 6000, 8000, 10000, 12000),
    labels=c("2e+3", "4e+3", "6e+3", "8e+3", "1e+4", "1.2e+4")
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Generation satisfactory solution found')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the generation a satisfactory solution is found.

```{r tor-exp-ssf-sum}
ssf = filter(sati_df, gen <= GENERATIONS & acro == 'exp')
ssf$acro = factor(ssf$acro, levels = TS_LIST)
ssf %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(gen)),
    min = min(gen, na.rm = TRUE),
    median = median(gen, na.rm = TRUE),
    mean = mean(gen, na.rm = TRUE),
    max = max(gen, na.rm = TRUE),
    IQR = IQR(gen, na.rm = TRUE)
  )
```

Kruskal–Wallis test illustrates evidence of statistical differences.

```{r tor-exp-ssf-kru}
kruskal.test(gen ~ T, data = ssf)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r tor-exp-ssf-wil}
pairwise.wilcox.test(x = ssf$gen, g = ssf$T, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

## Ordered exploitation results

Here we present the results for **best performances** found by each selection scheme parameter on the exploitation rate diagnostic.
50 replicates are conducted for each scheme explored.

### Performance over time

Best performance in a population over time.
Data points on the graph is the average performance across 50 replicates every 2000 generations.
Shading comes from the best and worse performance across 50 replicates.

```{r tor-ord-per-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'ord') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )
```

### Generation satisfactory solution found

First generation a satisfactory solution is found throughout the 50,000 generations.

```{r tor-ord-ssf, warning=FALSE, out.width="100%"}
plot = filter(sati_df, acro == 'ord') %>%
  ggplot(., aes(x = T, y = gen , color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Generation",
    limits=c(10000, 60000),
    breaks=c(10000, 20000, 30000, 40000,50000,60000),
    labels=c("1e+4","2e+4","3e+4","4e+4","5e+4","FAIL")
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Generation satisfactory solution found')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the generation a satisfactory solution is found.

```{r tor-ord-ssf-sum}
ssf = filter(sati_df, gen <= GENERATIONS & acro == 'ord')
ssf$acro = factor(ssf$acro, levels = TS_LIST)
ssf %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(gen)),
    min = min(gen, na.rm = TRUE),
    median = median(gen, na.rm = TRUE),
    mean = mean(gen, na.rm = TRUE),
    max = max(gen, na.rm = TRUE),
    IQR = IQR(gen, na.rm = TRUE)
  )
```

Kruskal–Wallis test illustrates evidence of statistical differences.

```{r tor-ord-ssf-kru}
kruskal.test(gen ~ T, data = ssf)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r tor-ord-ssf-wil}
pairwise.wilcox.test(x = ssf$gen, g = ssf$T, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 'l')
```

## Contradictory objectives results

Here we present the results for **activation gene coverage** and **satisfactory trait coverage** found by each selection scheme parameter on the contradictory objectives diagnostic.
50 replicates are conducted for each scheme parameters explored.

### Activation gene coverage over time

Activation gene coverage in a population over time.
Data points on the graph is the average activation gene coverage across 50 replicates every 2000 generations.
Shading comes from the best and worse coverage across 50 replicates.


```{r tor-con-act-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'con')  %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Activation gene coverage over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )
```

### Final activation gene coverage

Activation gene coverage found in the final population at 50,000 generations.

```{r tor-con-act-end, out.width="100%"}
plot = filter(over_time_df, gen == 50000 & acro == 'con') %>%
  ggplot(., aes(x = T, y = uni_str_pos, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 2),
    breaks=c(0,1,2)
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Final activation gene coverage')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the generation a satisfactory solution is found.

```{r tor-con-act-sum}
act_coverage = filter(over_time_df, gen == 50000 & acro == 'con')
act_coverage$acro = factor(act_coverage$acro, levels = TS_LIST)
act_coverage %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

### Satisfactory trait coverage over time

Satisfactory trait coverage in a population over time.
Data points on the graph is the average activation gene coverage across 50 replicates every 2000 generations.
Shading comes from the best and worse coverage across 50 replicates.


```{r tor-con-sat-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'con')  %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_uni_obj),
    mean = mean(pop_uni_obj),
    max = max(pop_uni_obj)
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 2),
    breaks=c(0,1,2)
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Satisfactory trait coverage over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )
```

### Final satisfactory trait coverage

Satisfactory trait coverage found in the final population at 50,000 generations.

```{r tor-con-sat-end, out.width="100%"}
plot = filter(over_time_df, gen == 50000 & acro == 'con') %>%
  ggplot(., aes(x = T, y = pop_uni_obj, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 2),
    breaks=c(0,1,2)
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Final satisfactory trait coverage')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the generation a satisfactory solution is found.

```{r tor-con-sat-sum}
sat_coverage = filter(over_time_df, gen == 50000 & acro == 'con')
sat_coverage$acro = factor(sat_coverage$acro, levels = TS_LIST)
sat_coverage %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(pop_uni_obj)),
    min = min(pop_uni_obj, na.rm = TRUE),
    median = median(pop_uni_obj, na.rm = TRUE),
    mean = mean(pop_uni_obj, na.rm = TRUE),
    max = max(pop_uni_obj, na.rm = TRUE),
    IQR = IQR(pop_uni_obj, na.rm = TRUE)
  )
```

## Multi-path exploration results

Here we present the results for **best performances** and **activation gene coverage** found by each selection scheme parameter on the multi-path exploration diagnostic.
50 replicates are conducted for each scheme parameter explored.

### Activation gene coverage over time

Activation gene coverage in a population over time.
Data points on the graph is the average activation gene coverage across 50 replicates every 2000 generations.
Shading comes from the best and worse coverage across 50 replicates.


```{r tor-mpe-act-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'mpe')  %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(uni_str_pos),
    mean = mean(uni_str_pos),
    max = max(uni_str_pos)
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Activation gene coverage over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )
```

### Final activation gene coverage

Activation gene coverage found in the final population at 50,000 generations.

```{r tor-mpe-act-end, out.width="100%"}
plot = filter(over_time_df, gen == 50000 & acro == 'mpe') %>%
  ggplot(., aes(x = T, y = uni_str_pos, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Coverage",
    limits=c(0, 15),
    breaks=c(0,5,10,15)
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Final activation gene coverage')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the generation a satisfactory solution is found.

```{r tor-mpe-act-sum}
act_coverage = filter(over_time_df, gen == 50000 & acro == 'mpe')
act_coverage$acro = factor(act_coverage$acro, levels = TS_LIST)
act_coverage %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(uni_str_pos)),
    min = min(uni_str_pos, na.rm = TRUE),
    median = median(uni_str_pos, na.rm = TRUE),
    mean = mean(uni_str_pos, na.rm = TRUE),
    max = max(uni_str_pos, na.rm = TRUE),
    IQR = IQR(uni_str_pos, na.rm = TRUE)
  )
```

Kruskal–Wallis test illustrates evidence of statistical differences.

```{r tor-mpe-act-kru-end}
kruskal.test(uni_str_pos ~ T, data = act_coverage)
```

Results for post-hoc Wilcoxon rank-sum test with a Bonferroni correction.

```{r tor-mpe-act-wil-end}
pairwise.wilcox.test(x = act_coverage$uni_str_pos, g = act_coverage$T, p.adjust.method = "bonferroni",
                     paired = FALSE, conf.int = FALSE, alternative = 't')
```

### Performance over time

Best performance in a population over time.
Data points on the graph is the average performance across 50 replicates every 2000 generations.
Shading comes from the best and worse performance across 50 replicates.

```{r tor-mpe-per-ot, warning=FALSE, out.width="100%"}
lines = filter(over_time_df, acro == 'mpe') %>%
  group_by(T, gen) %>%
  dplyr::summarise(
    min = min(pop_fit_max) / DIMENSIONALITY,
    mean = mean(pop_fit_max) / DIMENSIONALITY,
    max = max(pop_fit_max) / DIMENSIONALITY
  )

ggplot(lines, aes(x=gen, y=mean, group = T, fill = T, color = T, shape = T)) +
  geom_ribbon(aes(ymin = min, ymax = max), alpha = 0.1) +
  geom_line(size = 0.5) +
  geom_point(data = filter(lines, gen %% 2000 == 0 & gen != 0), size = 1.5, stroke = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_continuous(
    name="Generations",
    limits=c(0, 50000),
    breaks=c(0, 10000, 20000, 30000, 40000, 50000),
    labels=c("0e+4", "1e+4", "2e+4", "3e+4", "4e+4", "5e+4")
    
  ) +
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Performance over time')+
  p_theme +
  guides(
    shape=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    color=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize'),
    fill=guide_legend(nrow=2, title.position = "left", title = 'Tournament \nSize')
  )
```

### Best performance throughout

Best performance reached throughout 50,000 generations in a population.


```{r tor-mpe-per-bst, out.width="100%"}
plot = filter(best_df, var == 'pop_fit_max' & acro == 'mpe') %>%
  ggplot(., aes(x = T, y = val / DIMENSIONALITY, color = T, fill = T, shape = T)) +
  geom_flat_violin(position = position_nudge(x = .1, y = 0), scale = 'width', alpha = 0.2, width = 1.5) +
  geom_boxplot(color = 'black', width = .07, outlier.shape = NA, alpha = 0.0, size = 1.0, position = position_nudge(x = .16, y = 0)) +
  geom_point(position = position_jitter(width = 0.03, height = 0.02), size = 2.0, alpha = 1.0) +
  scale_y_continuous(
    name="Average trait score",
    limits=c(0, 100),
    breaks=seq(0,100, 20),
    labels=c("0", "20", "40", "60", "80", "100")
  ) +
  scale_x_discrete(
    name="Size"
  )+
  scale_shape_manual(values=SHAPE)+
  scale_colour_manual(values = cb_palette, ) +
  scale_fill_manual(values = cb_palette) +
  ggtitle('Best performance throughout')+
  p_theme

plot_grid(
  plot +
    theme(legend.position="none"),
  legend,
  nrow=2,
  rel_heights = c(3,1)
)
```

#### Stats

Summary statistics for the best performance.

```{r tor-mpe-per-sum}
performance = filter(best_df, var == 'pop_fit_max' & acro == 'mpe')
performance %>%
  group_by(T) %>%
  dplyr::summarise(
    count = n(),
    na_cnt = sum(is.na(val)),
    min = min(val / DIMENSIONALITY, na.rm = TRUE),
    median = median(val / DIMENSIONALITY, na.rm = TRUE),
    mean = mean(val / DIMENSIONALITY, na.rm = TRUE),
    max = max(val / DIMENSIONALITY, na.rm = TRUE),
    IQR = IQR(val / DIMENSIONALITY, na.rm = TRUE)
  )
```

Kruskal–Wallis test illustrates evidence of **no statistical differences**.

```{r tor-mpe-per-kru}
kruskal.test(val ~ T, data = performance)
```



