---
title: "Supplemental Material: Selection Scheme Parameter Sweep MVC Diagnostics"
author: "Jose Guadalupe Hernandez"
date: "`r Sys.Date()`"
output: bookdown::gitbook
documentclass: book
biblio-style: apalike
nocite: '@*'
link-citations: yes
github-repo:  jgh9094/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes
description: "Supplemental material for selection scheme parameter sweep with diagnostics and valleys."
---

```{r base-idx-init, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is the supplemental material for selection scheme parameter sweep experiments with diagnostics combined with valleys.

## About our supplemental material

This supplemental material is hosted on [GitHub](https://github.com) using GitHub pages.
The source code and configuration files used to generate this supplemental material can be found in [this GitHub repository](https://github.com/jgh9094/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes).
We compiled our data analyses and supplemental documentation into this nifty web-accessible book using [bookdown](https://bookdown.org/).

This supplemental material includes the following selection schemes:

- Truncation (Section \@ref(truncation-selection))
- Tournament (Section \@ref(tournament-selection))
- Genotypic fitness sharing (Section \@ref(genotypic-fitness-sharing))
- Phenotypic fitness sharing (Section \@ref(phenotypic-fitness-sharing))
- Nondominated sorting (Section \@ref(nondominated-sorting))
- Novelty search (Section \@ref(novelty-search))

## Contributing authors

- [Jose Guadalupe Hernandez](https://jgh9094.github.io/)
- [Alexander Lalejini](https://lalejini.com)
- [Charles Ofria](http://ofria.com)

## Computer Setup

These analyses were conducted in the following computing environment:

```{r base-com-ver}
print(version)
```


## Experimental setup

Setting up required variables variables.

```{r base-data-setup}
# libraries we are using
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)

# data diractory for gh-pages
DATA_DIR = '/opt/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes/DATA/PARAM_SWEEP/'

# data diractory for local testing
# DATA_DIR = '~/Desktop/Repositories/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes/DATA/PARAM_SWEEP/'

# graph variables
SHAPE = c(5,3,1,2,6,0,4,20,8)
cb_palette <- c('#332288','#88CCEE','#EE7733','#EE3377','#117733','#882255','#44AA99','#CCBB44', '#000000')
TSIZE = 26
p_theme <- theme(
  text = element_text(size = 19),
  plot.title = element_text( face = "bold", size = 20, hjust=0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  legend.title=element_text(size=13),
  legend.text=element_text(size=13),
  axis.title = element_text(size=19),
  axis.text = element_text(size=19),
  legend.position="bottom",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  linewidth = 0.5, linetype = "solid")
)

# default variables
DIMENSIONALITY = 100
GENERATIONS = 50000

# selection scheme params exploring
TR_LIST = c('1','2','4','8','16','32','64','128','256')
TS_LIST = c('2','4','8','16','32','64','128','256','512')
FS_LIST = c('0','0.1','0.3','0.6','1.2','2.5','5')
ND_LIST = c('0','0.1','0.3','0.6','1.2','2.5','5')
NS_LIST = c('1','2','4','8','15','30')
```