---
title: "Supplemental Material: Base Diagnostics"
author: "Jose Guadalupe Hernandez"
date: "`r Sys.Date()`"
output: bookdown::gitbook
documentclass: book
biblio-style: apalike
nocite: '@*'
link-citations: yes
github-repo:  jgh9094/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes
description: "Supplemental material for analyzing nondominated sorting by parts on the contradictory objectives diagnostic."
---

```{r base-idx-init, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is the supplemental material for experiments breaking down nondominated sorting into its two main components: phenotypic fitness sharing and nondominated front ranking.
We evaluated these components, along with standard nondominated sorting, on the contradictory objectives diagnostic to measure their contribution on the overall effectiveness of nondominated sorting.

## About our supplemental material

This supplemental material is hosted on [GitHub](https://github.com) using GitHub pages.
The source code and configuration files used to generate this supplemental material can be found in [this GitHub repository](https://github.com/jgh9094/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes).
We compiled our data analyses and supplemental documentation into this nifty web-accessible book using [bookdown](https://bookdown.org/).

Our supplemental material includes the following paper figures and statistics:

- Nondomintaed sorting breakdown (Section \@ref(nodominated-sorting-breakdown))

## Contributing authors

- [Jose Guadalupe Hernandez](https://jgh9094.github.io/)
- [Alexander Lalejini](https://lalejini.com)
- [Charles Ofria](http://ofria.com)

## Computer Setup

These analyses were conducted in the following computing environment:

```{r base-com-ver}
print(version)
```


## Experimental setup

Setting up required variables variables.

```{r base-data-setup}
# libraries we are using
library(ggplot2)
library(cowplot)
library(dplyr)
library(PupillometryR)

# data diractory for gh-pages
# DATA_DIR = '/opt/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes/DATA/CONTRADICTORY_NONDOMINATED/'

# data diractory for local testing
DATA_DIR = '~/Desktop/Repositories/ECJ-2023-Suite-Of-Diagnostic-Metrics-For-Characterizing-Selection-Schemes/DATA/CONTRADICTORY_NONDOMINATED/'

# graph variables
SHAPE = c(5,3,1)
cb_palette <- c('#88CCEE','#EE7733','#EE3377')
TSIZE = 26
p_theme <- theme(
  text = element_text(size = 28),
  plot.title = element_text( face = "bold", size = 22, hjust=0.5),
  panel.border = element_blank(),
  panel.grid.minor = element_blank(),
  legend.title=element_text(size=22),
  legend.text=element_text(size=23),
  axis.title = element_text(size=23),
  axis.text = element_text(size=22),
  legend.position="bottom",
  panel.background = element_rect(fill = "#f1f2f5",
                                  colour = "white",
                                  size = 0.5, linetype = "solid")
)

# default variables
REPLICATES = 50
DIMENSIONALITY = 100
GENERATIONS = 50000

# selection scheme related stuff
ACRO = c('nds','nfr','pfs')
NAMES = c('Nondominated sorting (nds)','Nondominated front ranking (nfr)','Phenotypic fitness sharing (pfs)')
```